```{r message=FALSE}
library(tidyverse)
```

## Synonyms from LPSN

LPSN covers the ranks of genus and species

```{r}
lpsn_synonyms <- read_csv("lpsn_synonyms.csv", col_types = "ccc") |>
  distinct(name, rank, correct_name)
```

```{r}
lpsn_synonyms |>
  count(rank)
```

Find any names that may resolve to more than one correct name.

```{r}
lpsn_synonyms |>
  group_by(name) |>
  filter(n() > 1)
```

Fix issues:

  * Bacillus pallidus is an illegitimate name for Falsibacillus pallidus,
    should resolve to Aeribacillus pallidus.

```{r}
lpsn_synonyms_unique <- lpsn_synonyms |>
  filter(!(
    (name %in% "Bacillus pallidus") &
      (correct_name %in% "Falsibacillus pallidus")))
```

Check again.

```{r}
lpsn_synonyms_unique |>
  group_by(name) |>
  filter(n() > 1)
```

## Synonyms from NCBI

```{r}
ncbi_synonyms <- read_csv("ncbi_synonyms.csv", col_types = "ccc")
```

```{r}
ncbi_synonyms |>
  count(rank)
```

Find any names that may resolve to more than one correct name.

```{r}
ncbi_duplicate_synonyms <- ncbi_synonyms |>
  group_by(name) |>
  filter(n() > 1) |>
  ungroup() |>
  arrange(name, rank)
ncbi_duplicate_synonyms
```

When a name could potentially resolve to more than one correct name at NCBI,
it resolves to two taxa, one at the phylum level and one at the class level.
Fix by always resolving to the phylum level.

```{r}
ncbi_duplicate_synonyms_fixed <- ncbi_duplicate_synonyms |>
  filter(rank %in% "phylum")
```

```{r}
ncbi_synonyms_unique <- ncbi_synonyms |>
  group_by(name) |>
  filter(n() == 1) |>
  ungroup() |>
  bind_rows(ncbi_duplicate_synonyms_fixed)
```

## Extra synonyms

Amazingly, Firmicutes is not listed as a synonym of Bacillota at NCBI

```{r}
extra_synonyms_unique <- read_csv("extra_synonyms.csv", col_types = "ccc")
```

## Combine synonym tables and export

```{r}
taxon_synonyms <- bind_rows(
  lpsn_synonyms_unique,
  ncbi_synonyms_unique,
  extra_synonyms_unique
)
```

```{r}
taxon_synonyms |>
  count(rank, sort = TRUE)
```

```{r}
usethis::use_data(taxon_synonyms, overwrite = TRUE)
```

